---
title: "Create datasets ready for model building"
author: Nederlandse Zorgautoriteit
date: August 2019
output:
  pdf_document:
    toc: true
    toc_depth: 3
---


# Load packages

```{r}
rm(list = ls())
library(ggplot2)
library(data.table)
```

# Set source directory

```{r}
# Read out DSID
ds_id <- as.integer(readLines("../ds_id.txt"))

suffix_name <- paste0("DSID_", sprintf("%0.2d", ds_id), "_")

dir_pilot <- readLines("../dir_pilot.txt")

```

# Source functions

```{r}
folder <- "functions"

files <- list.files(folder, pattern = "[.][rR]$", 
                        full.names = TRUE, recursive = TRUE)
if (!length(files))
    stop(simpleError(sprintf('No R files in folder "%s"', folder)))

src <- invisible(lapply(files, source))

message(sprintf('%s files sourced from folder "%s"', length(src), folder))

```


# Read data

```{r}
file_name <- paste0(dir_pilot, "Output/", suffix_name, "zorgpolissen.rds")
zorgpolissen <- setDT(readRDS(file_name))

file_name <- paste0(dir_pilot, "Output/", suffix_name, "features_zorgpolissen.rds")
features_zorgpolissen <- setDT(readRDS(file_name))

file_name <- paste0(dir_pilot, "Output/", suffix_name, "varlist_all.rds")
varlist_all <- setDT(readRDS(file_name))

```

# Read feature_set_list

This contains a list of all datasets for modelling to prepare.

```{r}
feature_sets_list <- data.table(read.csv2("../config/feature_sets_list.csv", 
                                   stringsAsFactors = FALSE))

# select subset for feature set construction
feature_sets_list_sub <- feature_sets_list[active == 1]

```

# Construct feature sets

THis part contains the code for particular filters. 
As an example we code the `ex_restitutie` filter.

This is also the place where feature sets for the different provider groups is made.
Since the example only contains a single provider group ("all") that part of the code is commented out.

```{r}
for(i in 1:nrow(feature_sets_list_sub)) {
  feature_set <- feature_sets_list_sub[i,]
  
  fs_id <- feature_set$fs_id
  fs_name <- paste0("FSID_", sprintf("%0.2d", fs_id), "_")
  
  #
  features_all <- features_zorgpolissen

  # filters
  if(feature_set$ex_restitutie == 1) {
    features_all <- features_all[soortpolis != "Restitutie"]
  }
  

  # save results
  dep_vars <- c('premie')
  indep_vars <- varlist_all$varname
  
  ## features_all
  indep_all <- colnames(features_all)[colnames(features_all) %in% indep_vars]
  features_all <- features_all[complete.cases(features_all[, c(dep_vars, indep_all), with = FALSE])]
  
  file_name <- paste0(dir_pilot, 'Output/', fs_name, suffix_name, 'features_all.rds')
  saveRDS(features_all, file_name)

  # dit is de plek om feature sets voor specifieke aanbieder groepen te saven  
}

```

