---
title: "Create features for zorgpolissen"
author: Nederlandse Zorgautoriteit
date: August 2019
output:
  pdf_document:
    toc: true
    toc_depth: 3
---

# Load packages

```{r}
rm(list = ls())

library(ggplot2)
library(tidyverse)
library(data.table)
library(caret)

```

# Set source directory

```{r}
dir_pilot <- readLines("../dir_pilot.txt")

```

# Read datasources list

```{r}
# Read out DSID
ds_id <- as.integer(readLines("../ds_id.txt"))

suffix_name <- paste0("DSID_", sprintf("%0.2d", ds_id), "_")

```

# Read data

```{r}
file_name <- paste0(dir_pilot, "Output/", suffix_name, "zorgpolissen.rds")
zorgpolissen <- setDT(readRDS(file_name))

```

# Source functions

```{r}
source("functions/addVarsToVarlist.R")

```

# Create features for zorgpolissen

Is al in het goede format.

```{r}
features_zorgpolissen <- zorgpolissen

features_zorgpolissen$X <- NULL
```



save features_zorgpolissen table

```{r}
file_name <- paste0(dir_pilot, 'Output/', suffix_name, "features_zorgpolissen.rds")
saveRDS(features_zorgpolissen, file_name)

```


# Add variable names and setname to variable list


We need to add all features, except `premie`, this is our dep var.

To showcase how groups of predictors work we do the following.

We split the predictors in two groups: variabelen gerelateerd aan de contracteergraad (zp_cgraad) en overig (zp_overig).


```{r}
zp_cgraad <- c( "CGApo"     ,   "CGFysio"  ,    "CGZbc"     ,   "CGZiekenhuis" )

empty_varlist <- data.table()
varlist_zp_cgraad <- addVarsToVarlist(empty_varlist, zp_cgraad)

```


```{r}
zp_overig <- names(features_zorgpolissen)

# geen voorspellers
exclude <- c("uzovi", "concern", "verz", "polisnr", "label", "Naammodelovereenkomst", "premie", "AanbiederID", "jaar")

zp_overig <-  setdiff(zp_overig, c(exclude, zp_cgraad))

varlist_zp <- addVarsToVarlist(varlist_zp_cgraad, zp_overig)
```

```{r}
zp_jaar <- "jaar"

varlist_zp <- addVarsToVarlist(varlist_zp, zp_jaar)
```


```{r}
# save
file_name <- paste0(dir_pilot, 'Output/', suffix_name, "varlist_all.rds")
saveRDS(varlist_zp, file_name)

```



