---
title: "Process fitted models"
output: pdf_document
---
# Prepare

## Load packages

```{r}
rm(list=ls())
library(data.table)
library(ggplot2)
library(rpart.plot)

options(scipen=999)
```

```{r}
# Read out DSID
ds_id <- as.integer(readLines("../ds_id.txt"))

suffix_name <- paste0("DSID_", sprintf("%0.2d", ds_id), "_")

dir_pilot <- readLines("../dir_pilot.txt")

```

# Read model list

```{r}
model_list <- data.table(read.csv2("../config/model_list.csv", 
                                   stringsAsFactors = FALSE))

model_list_sub <- model_list[active == 1]

# drop trailing empty cols X X.1 etc
cols_ids_to_drop <- grep("^X", colnames(model_list_sub))

model_list_sub <- model_list_sub[, !(cols_ids_to_drop), with = FALSE]
```

# Read feature set list

```{r}
feature_set_list <- data.table(read.csv2("../config/feature_sets_list.csv", 
                                   stringsAsFactors = FALSE))

feature_set_list_sub <- feature_set_list[active == 1]


```

# Read var sets

```{r}
varsets <- data.table(read.csv2("../config/var_sets.csv", 
                                   stringsAsFactors = FALSE))

varsets_sub <- varsets[is_active == 1]

```

# Source functions

```{r}
folder <- "functions"

files <- list.files(folder, pattern = "[.][rR]$", 
                        full.names = TRUE, recursive = TRUE)
if (!length(files))
    stop(simpleError(sprintf('No R files in folder "%s"', folder)))

src <- invisible(lapply(files, source))

message(sprintf('%s files sourced from folder "%s"', length(src), folder))

```


# Construct list of models to process

Construct list of models that were fitted in the `build_models.Rmd` Notebook.

Point `fit_folder` to location containing the fitted models.

```{r}
fit_folder <- c("..\\Work\\Output/")

model_res <- as.data.table(construct_model_filelist(model_list_sub, 
                                                    feature_set_list_sub, 
                                                    varsets_sub, 
                                                    aanb_list,
                                                    folder = fit_folder))

```

# Enrich with model_list en varsets records

```{r}
setkey(model_res, model_id)
setkey(model_list_sub, model_id)
model_res <- model_res[model_list_sub]

```


```{r}
model_res$var_set_id <- as.integer(as.character(model_res$var_set_id))

setkey(model_res, var_set_id)
setkey(varsets, var_set_id)
model_res <- varsets[model_res]

```

# Calculate metrics per model. Only for best model.

```{r}
model_res <- as.data.table(process_results(model_res))

```


## Creeër label per fit

```{r}
model_res$label2 <- paste0(model_res$fit_method, "_", 
                           model_res$metric, "_" , model_res$selectionFunction)

```


```{r}
table(is.na(model_res$meanMAPE))
```

```{r}
model_res <- model_res[, fit_id := paste0(fs_id, "_", ds_id, "_", model_id, "_", var_set_id, 
                                          ifelse(is.na(aanb_ex), "", paste0("_ex", aanb_ex)))]
```

# Plak aanbieder naam er aan

```{r eval = FALSE}
pilot_aanbieders <- as.data.table(read.csv2("../config/datasources_list.csv", na.strings = c("NULL")))

pilot_aanbieders <- subset(pilot_aanbieders, select = c(aanbiederID, provider))

setnames(pilot_aanbieders, "aanbiederID", "aanb_ex")
setnames(pilot_aanbieders, "provider", "AanbiederNaam")

setkey(model_res, aanb_ex)
setkey(pilot_aanbieders, aanb_ex)

model_res <- pilot_aanbieders[, .(aanb_ex, AanbiederNaam)][model_res]

model_res <- model_res[, AanbiederNaam := as.factor(AanbiederNaam)]
```

# Plak fset specs eraan

```{r}
setkey(model_res, fs_id)
setkey(feature_set_list, fs_id)
model_res <- feature_set_list[model_res]

```

# Save results

```{r}
saveRDS(model_res, "../Work/Output/model_res.rds")

```

# Plot all CART trees

```{r eval = FALSE}
for(filename in model_res[fit_method == "cart" & var_set_label != "intercept only",]$filename){
  
  caret_fit <- readRDS(filename)
  
  png_out_name <-   paste0(filename, "_tree.png")
  
  png(file = png_out_name, 
    width = 2*640, # The width of the plot in inches
    height = 2*480,
    pointsize = 18) # The height of the plot in inches
 
  plot_tree_model(caret_fit$finalModel)
  dev.off() 
}
```

